Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-11 paper.tex
Julia tried to mess up the structure a bit ...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				INTRODUCTION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Anthropomorphism}
\label{sec:intro}

@@

Phenomenons related to anthropomorphism -- along with questions such as "how
much human do we perceive in the non-human" or "how human-like do we treat
non-human artifacts" (and why?) -- have received remarkable attention in the
domains of Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI):
the study of humans interacting with an artificial system / machine. Following
the \textit{Media Equation}, it has been described that people mindlessly react
socially to computers \cite{reeves_media_1996} and may even attribute human
(social) characteristics to their artificial counterpart. The phenomenon has
also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von
der P{\"u}tten (2013)}, and more recent studies investigated how far people
ascribe personality or intentions to artificial emobdied agents or whether they
show empathetic behavior toward robots
\cite{rosenthal-vonderputten_experimental_2013}. The common base for this
research is the assumption that humans perceive or react to a non-human agent or
artifact as somewhat similar to a human.

@@

\paragraph{Anthropomorphism in robotics}
\hl{[I think this first paragraph should go somewhere else, later probably]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				ANTHROPOMORPHISM: EXPLANATIONS & BACKGROUND
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Anthropomorphism as a Social Phenomenon}
\label{sec:origins-anthropomorphism}

@@

\subsection{Explanations for Anthropomorphism}
\label{sec:explanations}

\fxfatal{inconsistency: we already give explanations for anthropomorphism in previous paragraph...}
According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main
perspectives in explaining people's tendency to anthropomorphize. The first
one explains anthropomorphism from the design of the artifact
(anthropomorphic form in the design). It assumes that humans directly
respond to life-like or social cues that an object or system emits, without
thoughtful mental processing, by simply applying stereotypes and heuristics
to it. In fact, from early childhood on, humans are inherently well-trained
to perceive life \cite{epley_seeing_2007}. Schmitz
\cite{schmitz_concepts_2011} describes that within the visual scope of
design, the outer appearance can have an important impact on the overall
perception of an object. The basic assumption here is that if an artifact
appears much like a human, it is likely to be treated similar to a human. If
this explanation of anthropomorphism is correct, people may respond
automatically to social cues emitted by a robot, and apply human-human
social schemas and norms to these interactions.

@@

\subsection{Insights from Social and Developmental Psychology}
\label{sec:psychological-factors}

@@

\subsection{Anthropomorphism in Robotics}
\label{sec:anthropomorphism-robotics}

\subsection{Anthropomorphism as a multi-layered phenomenon}
\label{sec:3.4}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				DOES ANTHROPOMORPHISM MAKE ROBOTS MORE SOCIAL?
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Does anthropomorphism make robots more social?}
\label{sec:more_social}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				DYNAMICS OF ANTHROPOMORPHISM
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{A Model of the Dynamics of Anthropomorphism}
\label{sec:dynamics_model}

\subsection{Why is anthropomorphism likely to change over time?}
\label{sec:whychanges}

@@

\subsection{Model of anthropomorphism over time}
\label{sec:modelintro}

@@

\subsection{Three phases}
\label{sec:phases}

@@

\subsection{Initialization Phase}
\label{sec:initialization}

@@

\subsection{Familiarization Phase}
\label{sec:familiarization}

@@

\subsection{Stabilization Phase}
\label{sec:stabilization}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				DISCUSSION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:discussion}

@@

\section{Cognitive Interpretations}
\label{sec:cognitivemodel}

@@

\subsection{Explanations for anthropomorphism}

\subsection{Cognitive Processes and Phases}

@@

\subsection{Relation to the model of anthropomorphism}

@@

\subsection{Effect of Context of Use and Purpose of the Robot}
\label{sec:8.1}
Frederic: role of uselessness

\begin{itemize}
    \item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot
        is impacted by the context of use and purpose of the robot. A social
        context and purpose of the robot increases anthropomorphism.
        \textit{(context and purpose of the robot)}

\end{itemize}

\subsection{Impact of the behavioral complexity of robots}

@@

\subsection{Segmentation of interaction phases}

@@

\subsection{Behavioral cues of anthropomorphism}
\label{sec:behavioralcues}

@@

\subsection{Effect of Time and Familiarization}
\label{sec:8.2}

@@

\begin{itemize}
	\item[\textbf{Hypothesis 2}] A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{itemize}

@@

\subsection{Personal characteristic effects in anthropomorphizing}
\label{sec:8.3}

\subsection{Role of disruptive behaviors}
\label{sec:disruptive}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				CONCLUSION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

@@

\section{Conclusion}
\label{sec:conclusion}

@@

While anthropomorphism is traditionally empirically understood as the
interactions between the anthropomorphic design of a robot and the psychological
determinants of the user, it appears that the duration and context of the
interaction are also key factors, and that anthropomorphism needs to be
understood as a dynamic phenomenon. In this article, we propose a new formal
model of anthropomorphism that accounts for these three factors and also
explicits the dynamics of anthromorphism. We introduce the concepts of
\emph{initial} and \emph{stabilized levels of anthropomorphism} as compound
factors to characterize the profile of a given anthropomorphic interaction.

@@

\section*{Acknowledgements}

We would like to acknowledge here the fruitful discussions with A Jung Moon and
Aude Billard.

@@

\section{Bibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		INTRODUCTION & OVERVIEW
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% JULIA: brief problem definition / issue, motivation, objectives, contribution ...

\vspace{2cm}
\section{Introduction and Overview}
\label{sec:intro}

@@

Phenomenons related to anthropomorphism -- along with questions such as "how
much human do we perceive in the non-human" or "how human-like do we treat
non-human artifacts" (and why?) -- have received remarkable attention in the
domains of Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI):
the study of humans interacting with an artificial system / machine. Following
the \textit{Media Equation}, it has been described that people mindlessly react
socially to computers \cite{reeves_media_1996} and may even attribute human
(social) characteristics to their artificial counterpart. The phenomenon has
also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von
der P{\"u}tten (2013)}, and more recent studies investigated how far people
ascribe personality or intentions to artificial embodied agents or whether they
show empathetic behavior toward robots
\cite{rosenthal-vonderputten_experimental_2013}. The common base for this
research is the assumption that humans perceive or react to a non-human agent or
artifact as somewhat similar to a human.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		PART 1: WHAT OTHERS DID AND WE ALREADY KNOW ABOUT ANTHROPOMORPHISM
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% JULIA: there will be 4-5 subsections
%	1) anthropomorphism as a social phenomenon, definitions, origins, etc.
%	2) anthropomorphism as a consequence of anthropomorphic / life-like design
%	3) the link to robotics and HRI, mention the uncanny valley theory ...
%	4) however: we suggest anthropomorphism is more than a static feature ...
%
%

\vspace{2cm}
\section{Anthropomorphism}
\label{sec:anthropomorphism}

\hl{bridge sentence}

\subsection*{Anthropomorphism as a Social Phenomenon}
\label{sec:social-phenomenon}

@@

\paragraph{Explanations for Anthropomorphism}
\label{sec:explanations}

\fxfatal{inconsistency: we already give explanations for anthropomorphism in previous paragraph...}

According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main
perspectives in explaining people's tendency to anthropomorphize. The first
one explains anthropomorphism from the design of the artifact
(anthropomorphic form in the design). It assumes that humans directly
respond to life-like or social cues that an object or system emits, without
thoughtful mental processing, by simply applying stereotypes and heuristics
to it. In fact, from early childhood on, humans are inherently well-trained
to perceive life \cite{epley_seeing_2007}. Schmitz
\cite{schmitz_concepts_2011} describes that within the visual scope of
design, the outer appearance can have an important impact on the overall
perception of an object. The basic assumption here is that if an artifact
appears much like a human, it is likely to be treated similar to a human. If
this explanation of anthropomorphism is correct, people may respond
automatically to social cues emitted by a robot, and apply human-human
social schemas and norms to these interactions.

@@

\paragraph{Insights from Social and Developmental Psychology}
\label{sec:psychological-factors}

@@

\subsection*{Anthropomorphic Design Principle}
\label{sec:anthropomorphic-design}

\hl{check if we really need this section ... maybe yes because it is important for the uncanny valley hypothesis}

@@

\subsection*{Anthropomorphism in Robotics and Human-Robot Interaction}
\label{sec:anthropomorphism-robotics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				PART 2: OUR IDEAS -- A DYNAMIC PHENOMENON
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% SEVERIN & JULIA: there will be 2-3 subsections in which we present our ideas:
% 	1) anthropomorphism is a multi-factor phenomenon (the figure with the several factors)
%	2) anthropomorphism is dynamic (the dynamic curve model)
%
%

\vspace{2cm}
\section{Anthropomorphism as a multi-factor phenomenon that evolves over time}
\label{sec:our-ideas}

\hl{bridge sentence}

\subsection*{Multiple factors of anthropomorphism}
\label{sec:multi-factors}

\subsection*{A Model of the Dynamics of Anthropomorphism}
\label{sec:dynamics-model}

\paragraph{Why is anthropomorphism likely to change over time?}
\hl{maybe we need to move this paragraph to PART 3}

@@

@@

\subsection*{Three phases}
\label{sec:phases}

@@

\subsection*{Initialization Phase}
\label{sec:initialization}

@@

\subsection*{Familiarization Phase}
\label{sec:familiarization}

@@

\subsection*{Stabilization Phase}
\label{sec:stabilization}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		PART 3: EXPLANATIONS -- COGNITIVE CORRELATES, NEUROSCIENCE VIEW
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CLAIRE & SEVERIN:
%
%

\vspace{2cm}
\section{Cognitive Correlates and Neuroscience Perspective}
\label{sec:cognition-neuroscience}

@@

\subsection*{Cognitive Interpretations}
\label{sec:cognitive-model}

@@

\subsection*{Cognitive Processes and Phases}

@@

\subsection*{Relation to the model of anthropomorphism}

@@

\begin{itemize}
    \item \textbf{Hypothesis 1} A person's tendency to anthropomorphize a robot
        is impacted by the context of use and purpose of the robot. A social
        context and purpose of the robot increases anthropomorphism.
        \textit{(context and purpose of the robot)}
	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{itemize}

\subsection*{Impact of the behavioral complexity of robots}

@@

\subsection*{Segmentation of interaction phases}

@@

\subsection*{Behavioral cues of anthropomorphism}
\label{sec:behavioralcues}

@@

\subsection*{Effect of Time and Familiarization}

@@

\begin{itemize}
	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{itemize}

@@

\subsection*{Role of disruptive behaviors}
\label{sec:disruptive}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				DISCUSSION + FUTURE WORK
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
% CLAIRE: FMRI study idea

\vspace{2cm}
\section{Discussion}
\label{sec:discussion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				CONCLUSIONS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% JULIA & SEVERIN

\vspace{2cm}
\section{Conclusion}
\label{sec:conclusion}

@@

While anthropomorphism is traditionally empirically understood as the
interactions between the anthropomorphic design of a robot and the psychological
determinants of the user, it appears that the duration and context of the
interaction are also key factors, and that anthropomorphism needs to be
understood as a dynamic phenomenon. In this article, we propose a new formal
model of anthropomorphism that accounts for these three factors and also
explicits the dynamics of anthropomorphism. We introduce the concepts of
\emph{initial} and \emph{stabilized levels of anthropomorphism} as compound
factors to characterize the profile of a given anthropomorphic interaction.

@@

\vspace{2cm}
\section*{Acknowledgments}

We would like to acknowledge the fruitful discussions with A Jung Moon and
Aude Billard.

@@

\vspace{2cm}
\section*{Bibliography}
